---
title: "Weight of Fish"
author: "Galilea Hernandez"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


## Perch

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottom",main="Adjusted R^2")
```


This data shows us that Height and Weight are the best models. 

### Best Models
```{r}
which.max(summary.out$adjr2)
```

This shows that model 2 best expresses the data when we see the adjusted r squared value.

### Best Two regressor model

```{r}
summary.out$which[2,]
```

The best regressor model is model 2, this indicates that model 2 has the highest adjusted r- squared and two variables.


## Pike

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

The best model appears to be the one that include L1, L2, L3, H and W, and the best two regressor model appears to be model 2.

### Best Models

```{r}
which.max(summary.out$adjr2)
```

This indicates that the best model for Pike is the model with 5 variables.

### Best Two regressor model

```{r}
summary.out$which[2,]
```

We see that length 1 and length 3 are the two best regressor models, meaning they have the highest adjusted r squared value. Using leaps we were able to obtain the adjusted r-squared value. This gives us only the highest of adjusted r-squared values for 1, 2, 3, 4 and 5 variables for pike. 

## Roach

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomleft",main="Adjusted R^2")
```

The best model is the model with 2 variables. L3 and W have the hghest adjusted r squared

### Best Models

```{r}
which.max(summary.out$adjr2)
```

The model with two variables is the best model based off of leaps and the highest adjusted r-squared value. The two variables in the leaps model is L3 and W.


### Best Two regressor model

```{r}
summary.out$which[2,]
```

Leaps tells us the model with the highest adjusted r-squared value has two variables which are L3 and W. So the best two regressor model is the model that has L3 and


## Final Summary Statements

We used the leaps anova to establish the best regression model for three different fish, Perch, Pike, and Roach. For every fish we were able to determine which 2 regressor models had the highest adjusted r squared value that we calculated from using the leaps anova.

